\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}

\definecolor{primary}{gray}{0}
\definecolor{secondary}{gray}{0.4}
\definecolor{highlight}{gray}{0}

\hypersetup{
    colorlinks=true,
    urlcolor=black,
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\vspace{2pt}\titlerule]
\titleformat{\subsection}{\bfseries\color{primary}}{}{0em}{}

\begin{document}

%===== Header =====
\begin{center}
    {\Huge \textbf{Mohammad Azahruddin Ansari}} \\
    \vspace{4pt}
    {\large \textcolor{highlight}{Senior Android Engineer}} \\
    \vspace{6pt}
    \small
    \faMapMarker \hspace{1mm} Varanasi, UP, India \quad
    \faPhone \hspace{1mm} +91-9511446571 \quad
    \faEnvelope \hspace{1mm} \href{mailto:azhar17@live.com}{azhar17@live.com} \\
    \faLinkedin \hspace{1mm} \href{https://www.linkedin.com/in/iamazhar/}{linkedin.com/in/iamazhar} \quad
    \faGithub \hspace{1mm} \href{https://github.com/AzharCodeWizard}{github.com/AzharCodeWizard} \quad
    \faMedium \hspace{1mm} \href{https://medium.com/@iam_azhar}{medium.com/@iam\_azhar}
\end{center}

\vspace{8pt}

%===== Professional Summary =====
\section*{Professional Summary}
Versatile and impact-driven \textbf{Senior Android Engineer} with over \textbf{5.6 years} of experience developing high-traffic Android apps across telecom, fintech, and utility domains. Proven track record in leading architecture revamps, delivering robust SDKs, and optimizing performance for apps serving \textbf{500M+ users}. Adept in Kotlin, Jetpack Compose, modular design, and agile practices. Passionate about scalable systems, mentoring, and business-driven engineering.

%===== Skills =====
\section*{Skills}
\textbf{Languages \& Frameworks:} Kotlin, Java, Jetpack Compose, React Native \\
\textbf{Architecture:} MVVM, Clean Architecture, Modularization, Hilt, SOLID Principles \\
\textbf{Performance \& Debugging:} LeakCanary, Crashlytics, Profiler, ANR \& memory resolution \\
\textbf{Tooling \& CI/CD:} Git, GitHub/GitLab, Firebase CI/CD, Jenkins, Fastlane \\
\textbf{Analytics:} Firebase Analytics, Mixpanel, WebEngage, CleverTap \\
\textbf{Collaboration:} Agile/Scrum, Sprint Planning, Design Reviews, Mentorship \\
\textbf{Databases:} Room, SQLite, Firebase Realtime DB, Firestore

%===== Experience =====
\section*{Experience}

\textbf{Senior Software Engineer} \hfill Gurugram, India \\
\textit{Airtel} \hfill \textcolor{secondary}{Jul 2022 -- Present}
\begin{itemize}[left=0pt, label=\textbullet, itemsep=4pt]
    \item Designed and launched the \textbf{Safety Connect SDK} using Kotlin and MVVM, enabling real-time alerts; earned internal innovation awards.
    \item Integrated \textbf{Google Play Integrity API}, reducing fraud by \textbf{70\%} and boosting app security.
    \item Migrated app journeys to \textbf{channel-based architecture (BEFE)}; enabled dynamic feature delivery decoupled from app releases.
    \item Developed multiple features and acquisition journeys using \textbf{Jetpack Compose} with scalable and reusable UI components.
    \item Reduced release delays by decoupling deployment from release cycles, accelerating go-to-market by \textbf{2x}.
    \item Mentored \textbf{4+ engineers}, improving delivery velocity by \textbf{30\%} through clean code and best practices.
    \item Independently delivered scalable modules for \textbf{Mitra, MBOSS, GOAL, ECAF, Airtel Works}, impacting millions of users.
    \item Contributed to cross-platform efforts (React.js, iOS), enabling unified feature parity across ecosystems.
\end{itemize}


\textbf{Software Development Engineer} \hfill Delhi, India \\
\textit{Baazi Games} \hfill \textcolor{secondary}{Sep 2021 -- May 2022}
\begin{itemize}[left=0pt, label=\textbullet, itemsep=4pt]
    \item Developed \textbf{SpotsX feature from scratch using Jetpack Compose}, delivering a modern and modular UI experience.
    \item Migrated 70\% of codebase from Java to Kotlin in BalleBaazi app, enhancing stability and maintainability.
    \item Built features with analytics and secure payment flows, improving user engagement and onboarding completion.
    \item Led technical sessions and reviews, advancing Android skills across the team.
\end{itemize}

\textbf{Software Engineer} \hfill Noida, India \\
\textit{Patch InfoTech Pvt Ltd.} \hfill \textcolor{secondary}{Dec 2020 -- Sep 2021}
\begin{itemize}[left=0pt, label=\textbullet, itemsep=4pt]
    \item Developed core modules of \textbf{JioOnline} app under tight deadlines, collaborating across teams.
    \item Enhanced UX and backend integrations, boosting responsiveness across devices.
    \item Proactively resolved production issues to ensure high app availability and reliability.
\end{itemize}

\textbf{Software Engineer} \hfill India \\
\textit{Nirmal Labs} \hfill \textcolor{secondary}{Oct 2019 -- Dec 2020}
\begin{itemize}[left=0pt, label=\textbullet, itemsep=4pt]
    \item Built and deployed \textbf{30+ mini apps} (e.g., Quick Scanner, BharatVPN) reaching thousands of users.
    \item Diagnosed and fixed critical bugs in live apps using structured logs and crash reports.
\end{itemize}


%===== Key Projects =====
\section*{Key Projects}
\textbf{My Ummah} – Islamic lifestyle app with Jetpack Compose UI, prayer times, Qibla, Duas, and Zakat calculator. \\
\textbf{Quick Scanner} – PDF and image scanner app using OpenCV and Camera2 API. \\
\textbf{Send It} – WiFi-based offline file sharing app using QR and RoomDB. \\
\textbf{Boost360} – E-commerce platform that enabled \textbf{35,000+ SMBs} to launch digital storefronts. \\
\textbf{Plog (COVID Tracker)} – Contact tracing app using Bluetooth proximity + Google Maps SDK. \\
\textbf{Bharat VPN} – Secure VPN client leveraging OpenVPN with global server support. \\
\textbf{Dumb Charades (Game)} – Multiplayer guessing game with real-time Firebase backend.

%===== Education =====
\section*{Education}
\textbf{Kashi Institute of Technology, Varanasi} \hfill India \\
B.Tech in Computer Science and Engineering \hfill \textcolor{secondary}{Graduated Jan 2019}

\end{document}
